%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.5 in,top=0.5in,right=0.6 in,bottom=0.6in]{geometry} % Document margins
\usepackage[colorlinks,allcolors=blue]{hyperref}

\usepackage{lastpage, fancyhdr}
\fancyhead{}
\fancyfoot{}
\lfoot{\textit{Curriculum Vitae} -- {\sc Samuel M. Factor}}
\rfoot{\textit{page \thepage\ of \pageref*{LastPage}}}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0.5pt}

\fancypagestyle{plain}{
\fancyhf{} % clear all header and footer fields 
\fancyfoot[C]{\textit{page \thepage\ of \pageref*{LastPage}}} 
\renewcommand{\headrulewidth}{0pt} 
\renewcommand{\footrulewidth}{0pt}}
\setlength{\headheight}{5pt} 


%\pagestyle{fancy}
%\fancyhf{}
%\rfoot{PAGE \thepage}
%\lhead{Samuel M. Factor}
%\renewcommand{\headrulewidth}{0pt}

\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\name{Samuel M. Factor} % Your name
\address{Univ. of Texas at Austin Dept. of Astronomy, 2515 Speedway, Stop C1400, Austin, TX 78712} % Your address
\address{(608) 852-5853 \\ \href{mailto:sfactor@utexas.edu}{sfactor@utexas.edu} \\ \href{https://smfactor.github.io}{https://smfactor.github.io}}  % Your phone number and email
%\address{(608) 852-5853 \\ \href{mailto:sfactor@utexas.edu}{sfactor@utexas.edu} \\ \href{http://smfactor.github.io}{http://smfactor.github.io}}  % Your phone number and email
\address{\textit{{\huge Curriculum Vitae}}}

\def\changemargin#1#2{\list{}{\rightmargin#2\leftmargin#1}\item[]}
\let\endchangemargin=\endlist
\begin{document}

\pagestyle{fancy}
\thispagestyle{plain}
%\thispagestyle{empty}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

%\begin{rSection}{OBJECTIVE}

%{Recently graduated, multidisciplinary Engineer with excellent problem solving abilities and process-thinking skill seeks hands on experience within a company that embraces creativity and innovation.Through my studies, I have gained extensive knowledge of production and manufacturing engineering, product design, among many other components of  Mechanical Engineering.Effective communicator who builds positive, cohesive relationship with all level of staff, eager to put my extensive studies to practical, applied use.}


%\end{rSection}

%----------------------------------------------------------------------------------------

\begin{rSection}{Education}\itemsep -5pt
    {\bf Ph.D., Astronomy, The University of Texas at Austin} \hfill {Austin, TX 2023}
    \begin{itemize}
        \vspace{-5pt}
        \setlength\itemsep{-5pt}
        %\vspace{-5pt}
        \item[] Concentration in Communicating Science
        \item[] Dissertation Title: {\em Kernel-Phase Interferometry for Detection of Close in Companions:\\Demographics of Binary Brown Dwarfs from Birth to Maturity}, Advisor: Dr. Adam L. Kraus
    \end{itemize}
    \vspace{-5pt}
    
    {\bf M.A., Astronomy, Wesleyan University} \hfill Middletown, CT 2015
    \begin{itemize}
        \vspace{-5pt}
        \setlength\itemsep{-5pt}
        %\vspace{-5pt}
        \item[] Thesis Title: {\em ALMA Observations of Molecular Gas Emission from a Protoplanetary\\Disk in the Orion Nebula}, Advisor: Dr. A. Meredith Hughes
    \end{itemize}
    \vspace{-5pt}
    
    {\bf B.A., Physics and Computer Science, Wesleyan University} \hfill Middletown, CT 2014
    \begin{itemize}
        \vspace{-5pt}
        \setlength\itemsep{-5pt}
        %\vspace{-5pt}
        \item[] $\Phi BK$ Honor Society, GPA: 3.93
    \end{itemize}
    \vspace{-5pt}

    %{\bf The University of Texas at Austin}, Austin, TX
    %\begin{itemize}
    %    \vspace{-5pt}
    %    \setlength\itemsep{-5pt}
    %    \item[] {\bf Ph.D.}, Astronomy (Advisor: Dr. Adam Kraus) \hfill {2023}
    %    \begin{itemize}
    %        \vspace{-5pt}
    %        \setlength\itemsep{-5pt}
    %        \item[] Dissertation Title: {\em Kernel-Phase Interferometry for Detection of Close in Companions:\\Demographics of Binary Brown Dwarfs from Birth to Maturity}
    %    \end{itemize}
    %\end{itemize}
    %\vspace{-5pt}
    %
    %{\bf Wesleyan University}, Middletown, CT
    %\begin{itemize}
    %    \vspace{-5pt}
    %    \setlength\itemsep{-5pt}
    %    \item[] {\bf M.A.}, Astronomy (Advisor: Dr. A. Meredith Hughes) \hfill {2015}
    %    \begin{itemize}
    %        \vspace{-5pt}
    %        \setlength\itemsep{-5pt}
    %        \item[] Thesis Title: {\em ALMA Observations of Molecular Gas Emission from a Protoplanetary \\ Disk in the Orion Nebula}
    %    \end{itemize}
    %    \item[] {\bf B.A.}, Physics and Computer Science, $\Phi BK$ Honor Society, GPA: 3.93 \hfill {2014}
    %\end{itemize}
%\vspace{-5pt}
\end{rSection}

%----------------------------------------------------------------------------------------

\begin{rSection}{Research Experience}\itemsep -5pt  
    {\bf Postdoctoral Fellow} Advisor: Dr. Adam L. Kraus \hfill {2023--present}\\{\em Department of Astronomy, The University of Texas at Austin, Austin, TX}
    \vspace{-5pt}
    \begin{changemargin}{0in}{0.4in}
    \begin{itemize}
    \setlength\itemsep{-5pt}
\item Assessing the strengths, weaknesses, and best practice observing strategies for \emph{JWST} KPI imaging by calculating detection limits using archival calibration data.
    \end{itemize}
    \end{changemargin}

    {\bf Graduate Student Researcher} Advisor: Dr. Adam L. Kraus \hfill {2015--2023}\\{\em Department of Astronomy, The University of Texas at Austin, Austin, TX}
    \vspace{-5pt}
    \begin{changemargin}{0in}{0.4in}
    \begin{itemize}
    \setlength\itemsep{-5pt}
\item Applied an interferometric analysis technique to archival \emph{Hubble Space Telescope} (\emph{HST}) imaging to search for sub-stellar and planetary mass companions to nearby stars below the diffraction limit.
\item Analyzed the statistical demographics of companions in the field and young star-forming regions.
\item Analysis utilized the Lonestar5 \& 6 clusters at the Texas Advanced Computing Center (TACC).
    \end{itemize}
    \end{changemargin}

{\bf Graduate Student Researcher} Advisor: Dr. A. Meredith Hughes \hfill {2014--2015}\\{\em Astronomy Department, Wesleyan University, Middletown, CT}
    \vspace{-5pt}
    \begin{changemargin}{0in}{0.4in}
\begin{itemize}
    \setlength\itemsep{-5pt}
    \item Modeled the temperature and density structure of a protoplanetary disk based on molecular gas observations from the Atacama Large Millimeter/submillimeter Array (ALMA).
    \item Analysis utilized Wesleyan University's High Performance Compute Cluster.
\end{itemize} 
    \end{changemargin}

{\bf Undergraduate Research Assistant} Advisor: Dr. Fred Ellis \hfill {2012--2014}\\{\em Physics Department, Wesleyan University, Middletown, CT}
    \vspace{-5pt}
    \begin{changemargin}{0in}{0.4in}
    \begin{itemize}
    \setlength\itemsep{-5pt}
\item Built \& tested scattering properties of electronic LRC oscillator circuits modeling optical systems.
\item Research topics include: PT-symmetric systems, asymmetric wave transport, nonlinear systems.
\end{itemize} 
    \end{changemargin}

%\vspace{-5pt}
\end{rSection} 

%------------------------------------------------

\begin{rSection}{Honors \& Awards}\itemsep -5pt

    {\bf Board of Visitors Graduate Student Second Year Research Defense Award}, UT Austin \hfill {2017}\\
    {\bf Chambliss Astronomy Achievement Award}, Honorable Mention, AAS \hfill {Winter, 2016}\\
    {\bf Frank N. Edmonds, Jr. Memorial Fellowship in Astronomy}, UT Austin \hfill {2016}\\
    {\bf $\mathbf{\Phi}$BK}, Wesleyan University \hfill {Spring, 2014}\\
    {\bf Barry M. Goldwater Scholarship}, Honorable Mention \hfill {2013}\\
    {\bf Karl Van Dyke Prize}, Wesleyan University Physics Dept. \hfill {2013}\\
    {\bf Dean's List}, Wesleyan University \hfill {2010 - 2014}%\\
%\vspace{-5pt}
\end{rSection}

%------------------------------------------------------------------------

\begin{rSection}{Funding} \itemsep -5pt  

    {\em Kernel-Phase Detection Limits for Planet Discovery with JWST} \hfill {\$145,090}\\ PI of Cycle 1 James Webb Space Telescope Archival Research Grant 2509 \hfill 2021 
    
    {\em Discovery of Young Planetary Systems with Kernel-Phase Interferometry} \hfill {\$114,085}\\ PI of Cycle 29 Hubble Space Telescope Archival Research Grant 16612\hfill 2021

    {\em University Graduate Continuing Fellowship}\hfill {\$40,804}\\ The University of Texas at Austin Graduate School \hfill2018

    {\em Kernel-Phase Interferometry for Super-resolution Detection of Faint Companions}\hfill{\$141,430}\\ PI of Cycle 24 Hubble Space Telescope Archival Research Grant 14561 \hfill 2016
    
    {\em John W. Cox Graduate Excellence Fellowship}\hfill {\$18,000}\\ University of Texas at Austin Dept. of Astronomy recruiting Fellowship \hfill 2015

    {\em Travel to: 225th Meeting of the American Astronomical Society} \hfill {\$1,000}\\ Student Travel Grant, CT Space Grant College Consortium \hfill 2015
        
\vspace{-5pt}
\end{rSection} 

%----------------------------------------------------------------------------------

\begin{rSection}{Teaching Experience}\itemsep -5pt  

    {\bf \href{https://isee.ucsc.edu/programs/pdp/}{Professional Development Program}}, {\em Inst. for Scientist \& Engineer Educators} \hfill 2018, 2020(canceled)\\
    Intensive teaching workshop focusing on inquiry, assessment, and equity \& inclusion.

    {\bf Teaching Assistant} {\em Department of Astronomy, The University of Texas at Austin, Austin, TX}
    \vspace{-5pt}
    \begin{changemargin}{0.3in}{0in}
    AST 307: Introductory Astronomy, Prof. Brendan Bowler \hfill {Fall 2020}\\
    AST 376/392G: Observational Methods in Astronomy, Profs. A. Kraus \& S. Finkelstein \hfill {Fall 2018}\\
    AST 301: Introduction to Astronomy, Prof. John Scalo \hfill {Fall 2015}
    \end{changemargin}
    
    %{\bf Teaching Assistant} AST 307: Introductory Astronomy \hfill {Fall 2020}\\{\em Department of Astronomy, The University of Texas at Austin, Austin, TX}

    %{\bf Teaching Assistant} AST 376/392G: Observational Methods in Astronomy \hfill {Fall 2018}\\{\em Department of Astronomy, The University of Texas at Austin, Austin, TX}

    %{\bf Teaching Assistant} AST 301: Introduction to Astronomy \hfill {Fall 2015}\\{\em Department of Astronomy, The University of Texas at Austin, Austin, TX}

    {\bf Teaching Assistant} {\em Astronomy Department, Wesleyan University, Middletown, CT}
    \vspace{-5pt}
    \begin{changemargin}{0.3in}{0in}
    ASTR 107: The Universe, ASTR 211: Observational Astronomy, Prof. A. Meredith Hughes \hfill {2014, 2015}
    \end{changemargin}

    {\bf Course Assistant} {\em Computer Science and Physics Departments, Wesleyan University, Middletown, CT}
    \vspace{-5pt}
    \begin{changemargin}{0.3in}{0in}
    COMP 112: Intro. to Programming, Prof. James Lipton \hfill {Summer 2012}\\
    PHYS 215: Special Relativity, Prof. Fred Ellis \hfill {Fall 2013}
    \end{changemargin}
\vspace{-5pt}
\end{rSection}
 
%------------------------------------------------

\begin{rSection}{Outreach and Service} \itemsep -5pt

    {\bf Astronomy on Tap, Austin TX}, Organizing Committee and Speaker \hfill {2016--Present}\\Present free, accessible astronomy talks in a bar to $\sim300$ people monthly. Watch my talks on \href{https://smfactor.github.io/aboutme/}{my website}.

    {\bf Astrobites}, Author and Webmaster \hfill {2018--2019}\\Wrote brief paper summaries accessible to undergraduate level students. Read my posts on \href{http://astrobites.org/author/sfactor/}{astrobites.org}
    
    {\bf Graduate Student Observing Trip}, Trip Leader \hfill {2023}\\Co-lead trip to McDonald Observatory to teach early career graduate students about observing
    
    {\bf TAURUS Summer Program}, Observing Trip Committee, Webmaster, Informal Mentor \hfill {2017, 2019, 2021}\\Organized and lead the REU program's observing trip to McDonald Observatory.
    
    {\bf UT Austin Girl Day Festival}, Volunteer \hfill {2017, 2018, 2021, 2023}\\Facilitated hands on astronomy activities for over 8,000 middle school girls and their families.
    
    {\bf Astronomy Graduate Student Executive Committee}, UT Austin, Computer Officer \hfill{2017--2021}

    {\bf Ask an Astronomer}, Author, \href{http://askanastronomer.org/byauthor/?author=Sam+Factor}{askanastronomer.org}\hfill {2015--2016}%\\Answered questions from the public through \href{http://askanastronomer.org/byauthor/?author=Sam+Factor}{askanastronomer.org}

    {\bf Public Observing}, Van Vleck Observatory, Wesleyan University, Middletown, CT \hfill {2014--2015}%\\Helped host weekly public observing and kids nights.
\vspace{-5pt}    
\end{rSection}

%---------------------------------------------------------------------

\begin{rSection}{Programming Languages \& Software} \itemsep -3pt {}   
Python, Git, \LaTeX, MIRIAD, CASA, Mathematica, Fortran, C, Ruby, Rails, Java, Visual Basic, SML, Agda
%\vspace{-5pt}
\end{rSection}

%------------------------------------------------

%\vspace{1cm}
\begin{rSection}{Publications}\itemsep -3pt
%    \textbf{Samuel M. Factor} \& Adam L. Kraus, {\it in prep.}, ``ACS/HRC Kernel-Phase Interferometry I: First demonstration of KPI at visible wavelengths and Demographics of Young Brown Dwarfs in Taurus and Upper Scorpius"}

    \textbf{Samuel M. Factor}, 2023, Ph.D. Dissertation, \href{https://search.lib.utexas.edu/permalink/01UTAU_INST/9e1640/alma991058743782406011}{Kernel-phase interferometry for detection of close in companions: binary demographics of brown dwarfs from birth to maturity}
    
    \textbf{Samuel M. Factor} \& Adam L. Kraus, 2023, {\it AJ}, 165, 130, \href{https://ui.adsabs.harvard.edu/abs/2023AJ....165..130F}{``NICMOS Kernel-Phase Interferometry II: Demographics of Nearby Brown Dwarfs"}
    
    \textbf{Samuel M. Factor} \& Adam L. Kraus, 2022, {\it AJ}, 164, 244, \href{https://ui.adsabs.harvard.edu/abs/2022AJ....164..244F}{``NICMOS Kernel-Phase Interferometry I: Catalogue of Brown Dwarfs Observed in F110W and F170M"}
    
    \textbf{Samuel M. Factor}, A. M. Hughes, K. Flaherty, et al., 2017, {\it AJ}, 153, 233, \href{http://ui.adsabs.harvard.edu/abs/2017AJ....153..233F}{``ALMA Observations of Asymmetric Molecular Gas Emission from a Protoplanetary Disk in the Orion Nebula"} %R. K. Mann, J. Di Francesco, J. P. Williams, L. Ricci, B. C. Matthews, J. Bally, D. Johnstone
    
    S. Petrus et al. (incl. \textbf{S. Factor}, 43 of 121), 2024, {\it ApJL}, 966, L11, \href{https://ui.adsabs.harvard.edu/abs/2024ApJ...966L..11P}{``The JWST Early Release Science Program for Direct Observations of Exoplanetary Systems V: Do Self-Consistent Atmospheric Models Represent JWST Spectra? A Showcase With VHS 1256 b"}

    S. Sallum et al. (incl. \textbf{S. Factor}, 9 of 122), 2024, {\it ApJL}, 963, L2 \href{https://ui.adsabs.harvard.edu/abs/2024ApJ...963L...2S}{``The JWST Early Release Science Program for Direct Observations of Exoplanetary Systems IV. NIRISS Aperture Masking Interferometry Performance and Lessons Learned"}
    
    S. Ray et al. (incl. \textbf{S. Factor}, 12 of 123), submitted to ApJ Letters, \href{https://ui.adsabs.harvard.edu/abs/2023arXiv231011508R}{``The \textit{JWST} Early Release Science Program for Direct Observations of Exoplanetary Systems III: Aperture Masking Interferometric Observations of the star HIP\,65426 at 3.8$\mu$m"}
    
    A. Carter et al. (incl. \textbf{S. Factor}, 79 of 111), 2023, {\it ApJL}, 951, L20, \href{https://ui.adsabs.harvard.edu/abs/2023ApJ...951L..20C}{``The JWST Early Release Science Program for Direct Observations of Exoplanetary Systems I: High Contrast Imaging of the Exoplanet HIP 65426 b from 2-16 $\mu$m"}
    
    B. Miles et al. (incl. \textbf{S. Factor}, 80 of 111), 2023, {\it ApJL}, 946, L6, \href{https://ui.adsabs.harvard.edu/abs/2023ApJ...946L...6M}{``The JWST Early Release Science Program for Direct Observations of Exoplanetary Systems II: A 1 to 20 Micron Spectrum of the Planetary-Mass Companion VHS 1256-1257 b"}
    
    S. Hinkley et al. (incl. \textbf{S. Factor}, 46 of 89), 2022, {\it PASP}, 134, 095003, \href{https://ui.adsabs.harvard.edu/abs/2022PASP..134i5003H}{``The JWST Early Release Science Program for the Direct Imaging \& Spectroscopy of Exoplanetary Systems"}

    A. W. Mann et al. (incl. \textbf{S. Factor}, 10 of 14), 2019, {\it ApJ}, 871, 63, \href{https://ui.adsabs.harvard.edu/abs/2019ApJ...871...63M}{``How to Constrain Your M Dwarf. II. The Mass--Luminosity--Metallicity Relation from 0.075 to 0.70 Solar Masses"}

    %J. M. Lee, \textbf{S. Factor}, Z. Lin, I. Vitebskiy, F. Ellis, T. Kottos, \href{https://ui.adsabs.harvard.edu/abs/2014PhRvL.112y3902L}{``Reconfigurable directional lasing  modes in cavities with generalized $\mathcal{P}\tilde{\mathcal{T}}$ Symmetry,"} \emph{Phys. Rev. Lett.}, vol 112, p. 253902, Jun 2014
    J. M. Lee, \textbf{S. Factor}, Z. Lin, et al., \href{https://ui.adsabs.harvard.edu/abs/2014PhRvL.112y3902L}{``Reconfigurable directional lasing  modes in cavities with generalized $\mathcal{P}\tilde{\mathcal{T}}$ Symmetry,"} \emph{Phys. Rev. Lett.}, vol 112, p. 253902, Jun 2014

    %M. Chitsazi, \textbf{S.  Factor}, J. Schindler, H. Ramezani, F. M. Ellis and T. Kottos, \href{https://ui.adsabs.harvard.edu/abs/2014PhRvA..89d3842C}{``Experimental observation of lasing shutdown via asymmetric gain,"} \emph{Phys. Rev. A}, vol. 89, p. 043842, Apr 2014
    M. Chitsazi, \textbf{S.  Factor}, J. Schindler, et al., \href{https://ui.adsabs.harvard.edu/abs/2014PhRvA..89d3842C}{``Experimental observation of lasing shutdown via asymmetric gain,"} \emph{Phys. Rev. A}, vol. 89, p. 043842, Apr 2014

    %N. Bender, \textbf{S. Factor}, J. D. Bodyfelt, H. Ramezani, D. N. Christodulides, F. M. Ellis, and T. Kottos, \href{https://ui.adsabs.harvard.edu/abs/2013PhRvL.110w4101B}{``Observation of asymmetric transport in structures with active nonlinearities,"} \emph{Phys. Rev. Lett.}, vol. 110, p. 234101, June 2013
    N. Bender, \textbf{S. Factor}, J. D. Bodyfelt, et al., \href{https://ui.adsabs.harvard.edu/abs/2013PhRvL.110w4101B}{``Observation of asymmetric transport in structures with active nonlinearities,"} \emph{Phys. Rev. Lett.}, vol. 110, p. 234101, June 2013
    
\end{rSection}

%----------------------------------------------------------------------

\begin{rSection}{Presentations} \itemsep -3pt  
    Kernel-Phase Interferometry for Detection of Close in Companions: Binary Demographics of Brown Dwarfs from Birth to Maturity (talk number \href{https://ui.adsabs.harvard.edu/abs/2024AAS...24343204F}{432.04D}), \emph{243rd Meeting of the AAS}, January 2024, New Orleans, LA
    \vspace{-0.06cm}

    HST Kernel-Phase Interferometry: Binary Brown Dwarf Demographics from Birth to Maturity (\href{https://smfactor.github.io/assets/pubs/GMTposter.pdf}{poster}),\\\emph{Exoplanets: Atmospheres to Architectures, GMT Community Science Meeting}, Sep. 2023, Washington, DC
    \vspace{-0.06cm}
    
    Kernel-Phase Interferometry for Detection of Close in Companions: Binary Demographics of Brown Dwarfs from Birth to Maturity (\href{https://youtu.be/8vgoTbuspWs}{talk}), \emph{Public Ph.D. defense}, July 2023, Austin, TX
    \vspace{-0.06cm}
    
    HST Kernel-Phase Interferometry: Field-Age Brown Dwarf Population Demographics (\href{https://zenodo.org/record/7592115}{poster}),\\\emph{21st Cambridge Workshops of Cool Stars, Stellar Systems, and the Sun}, July 2022, Toulouse, France
    \vspace{-0.06cm}

    A NICMOS Kernel-Phase Interferometry Survey of Brown-Dwarf Binary Demographics (\href{https://www.cfa.harvard.edu/calendar/event/9287/}{invited talk}),\\\emph{CfA Stars \& Planets Seminar}, December 2021, Center for Astrophysics, Cambridge, MA
    \vspace{-0.06cm}
    
    A NICMOS Kernel-Phase Interferometry Survey of Brown-Dwarf Binary Demographics (invited talk),\\\emph{Stars and Planets Lunch And Talks (SPLAT)}, November 2021, Institute for Astronomy, Manoa, HI
    \vspace{-0.06cm}
    
    A NICMOS Kernel-Phase Interferometry Survey of Brown-Dwarf Binary Demographics (\href{https://drive.google.com/file/d/1vVPNLd2eT12pVJnRhTFYX5jqAVCRl_wg/view}{talk}),\\\emph{\href{https://sites.google.com/uci.edu/virtualmaskinghackathon/home}{Virtual Masking Hackathon}}, July 2021, Virtual
    \vspace{-0.06cm}
    
    Kernel-Phase Interferometry for Super-Resolution Detection of Faint Companions (\href{http://smfactor.github.io/assets/pubs/CS20p5Poster.pdf}{poster}), \\\emph{20.5th Cambridge Workshops of Cool Stars, Stellar Systems, and the Sun}, March 2021, Virtual 
    \vspace{-0.06cm}
    
    Kernel-Phase Interferometry for Super-Resolution Detection of Faint Companions (\href{http://smfactor.github.io/assets/pubs/ESSIVPoster.pdf}{poster}), \\\emph{Extreme Solar Systems IV}, August 2019, Reykjavik, Iceland 
    \vspace{-0.06cm}

    Kernel-Phase Interferometry for Super-Resolution Detection of Faint Companions (\href{http://smfactor.github.io/publications/CS20Poster.pdf}{poster}),\\\emph{Stars: Birth and Death, 6th Annual GMT Community Science Meeting}, September 2018, Honolulu, HI
    \vspace{-0.06cm}

    Kernel-Phase Interferometry for Super-Resolution Detection of Faint Companions (\href{http://smfactor.github.io/publications/CS20Poster.pdf}{poster}),\\\emph{20th Cambridge Workshop of Cool Stars, Stellar Systems, and the Sun}, August 2018, Boston, MA
    \vspace{-0.06cm}

    Kernel-Phase Interferometry for Super-Resolution Detection of Faint Companions (\href{http://smfactor.github.io/publications/SPF2Poster.pdf}{poster}),\\\emph{Star and Planet Formation in the Southwest 2}, March 2018, Oracle, AZ
    \vspace{-0.06cm}
    
    Are we alone? Finding and characterizing planets around other stars (invited talk),\\\emph{McDonald Observatory Board of Visitors Recruiting Event}, February, 2018, Houstion, TX
    \vspace{-0.06cm}

    Kernel-Phase Interferometry for Super-Resolution Detection of Faint Companions (\href{http://smfactor.github.io/publications/AASposter.pdf}{poster} number \href{http://adsabs.harvard.edu/abs/2017AAS...23011803F}{118.03}),\\\emph{230th Meeting of the AAS}, June 2017, Austin, TX
    \vspace{-0.06cm}

    Kernel-Phase Interferometry for Super-Resolution Detection of Faint Companions (\href{http://smfactor.github.io/publications/AASposter.pdf}{poster} number \href{http://adsabs.harvard.edu/abs/2017AAS...22914625F}{146.25}),\\\emph{229th Meeting of the AAS}, January 2017, Grapevine, TX (Chambliss Honorable Mention)
    \vspace{-0.06cm}

    \texttt{Git} is great! (\href{https://ottostruve.github.io/gsps/slides/factor_git.pdf}{slides}),\\{\em UT Austin Graduate Student Postdoc Seminar}, November 2016, Austin, TX
    \vspace{-0.06cm}

    Kernel-Phase Interferometry for Super-Resolution Detection of Faint Companions (\href{http://smfactor.github.io/publications/SSWposter.pdf}{poster}),\\\emph{Sagan Exoplanet Summer Workshop}, July 2016, Pasadena, CA
    \vspace{-0.06cm}

    %ALMA Observations of Molecular Gas Emission from a Protoplanetary Disk in the Orion Nebula Cluster (\href{http://smfactor.github.io/publications/WesPoster2.pdf}{poster}), \emph{Frank N. Bash Symposium}, October 2015, Austin, TX
    %\vspace{-0.06cm}

    Characterizing a Young Protoplanetary Disk in the Orion Nebula Cluster (\href{http://smfactor.github.io/publications/WesPoster.pdf}{poster} number \href{http://adsabs.harvard.edu/abs/2015AAS...22534906F}{349.06}),\\\emph{225th Meeting of the American Astronomical Society}, January 2015, Seattle, WA
    \vspace{-0.06cm}

%\vspace{0.7cm}
\end{rSection}

%------------------------------------------------

\begin{rSection}{Observing Experience} \itemsep -5pt
    JWST Cycle 1 (Archival)\hfill (see Funding)\\
    HST NICMOS, ACS, Cycle 24, 29 (Archival)\hfill (see Funding)\\
    0.8m Telescope, PFC, McDonald Observatory (P.I. Observing Course) \hfill{$>$30 nights}\\
    %0.9m Telescope, eyepiece, McDonald Observatory (P.I. Graduate Student Course) \hfill{4 nights}\\
    Harlan J. Smith 2.7m, DIAFI, McDonald Observatory (P.I. TAURUS, Observing Course) \hfill{4 nights}\\
    HJS 2.7m, GCMS (VIRUS-P), McDonald Observatory (P.I. TAURUS) \hfill{3 nights}\\
    HJS 2.7m, Tull Coude Spectrograph (TS23), McDonald Obs. (P.I. A. Rizzuto, Observing Course) \hfill{12 nights}\\
    Keck II, NIRC2 LGS, Mauna Kea Observatory, (P.I. A. Mann) \hfill{1 night}

\vspace{-5pt}
\end{rSection}

%----------------------------------------------------------------------
%\begin{rSection}{Memberships} \itemsep -3pt {}   
%    Junior Member, American Astronomical Society \hfill{2015--Present}
%\end{rSection}

%------------------------------------------------

\begin{rSection}{Extracurricular Activities} \itemsep -5pt  
{\bf Volunteer Coach}, Austin Rowing Club \hfill {2017--Present}\\
{\bf Certified Open Water Diver}, PADI (28 dives, 20 hours)\hfill {2013--Present}\\
{\bf Volunteer Assistant Coach}, Wesleyan University Men's Varsity Rowing \hfill {Fall, 2015}\\
{\bf Wesleyan University Men's Varsity Rowing} \hfill{2010--2014}
\begin{itemize}
\vspace{-6pt}
    \setlength\itemsep{-4pt}
All Sportsmanship Team, New England Small College Athletic Conference \hfill {2014}\\
All Academic Team, New England Small College Athletic Conference \hfill {2012--2014}\\
Stewards' All Academic Team, Eastern College Athletic Conference \hfill {2012--2014}\\
%NERC Men's JV 8+, 3rd place (2013, 2014), HOCR Men's Collegiate 8+, 5th place (2013)\\
%New England Rowing Championships Men's JV 8+, 3rd place \hfill {2013, 2014}\\
%Head of the Charles Men's Collegiate 8+, 5th place \hfill {2013}\\
\end{itemize}
%{\bf Assistant Coach}, Camp Randall Rowing Club, Madison WI \hfill {2011}\\
%{\bf Youth Paddling Instructor}, Rutabaga Paddlesports Outdoor Programs, Madison, WI \hfill {2010 - 2011}
%{\bf National Outdoor Leadership School}, alumni\hfill {2009}
\end{rSection}

\vspace{-25pt}
\vfill
{\scriptsize Last updated \today}
\vspace{-10pt}
\end{document}
